surfing

### 2021-05-09 inst/surfing.Rmd
consistentification

```{r}
players <- read.table("players.txt",header=TRUE)
head(players)
table(players$nation)
players$name
wildcards <- players$name[-(1:36)]
wildcards
```

@@

```{r,label=savesurfiningingdataset}
save(surfing,surfing_maxp,file="surfing.rda")
```

>>>>

```{r}
players <- read.table("wct_surfers_table.txt",header=TRUE)
head(players)
table(players$nation)
players$name
wildcards <- players$name[-(1:36)]
wildcards
```

@@

```{r,label=savesurfiningingdataset}
surfing_table <- players
save(surfing,surfing_maxp,surfing_table,file="surfing.rda")
```
